Paper Plots V2

### 2025-02-28 Rmd/paper_plots/paper_plots_1.3.Rmd
add paper plots version and min(20) scenarios

@@

## Optimize Sampling
### * Time series Expansion X Samples 10, 20, 30
```{r, fig.width=9, fig.height=5}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.2_ISS_500_iters_2025-01-28.RDS")

>>>>

# save out_1.4 for Steve to plug into the assessment
out_1.4$length$iss %>% 
  select(YEAR, iss) %>% 
  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)

@@

## Optimize Sampling

### Min 20
```{r, fig.width=9, fig.height=5}
out_26.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_26.1_ISS_500iters_output_2025-02-27.RDS")

year = out_26.1$length$iss$YEAR

df = tidytable(year = year,
               iss.base = out_1.4$length$iss$iss,
               iss.20.min = out_26.1$length$iss$iss)

df %>% 
  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
  filter(year%in%1999:2023) %>% 
  select(ISS.error) %>% 
  boxplot()

df %>% 
  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
  filter(year%in%2023) %>% 
  select(ISS.error) %>% 
  boxplot()

# df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

### * Time series Expansion X Samples 10, 20, 30
```{r, fig.width=9, fig.height=5}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.2_ISS_500_iters_2025-01-28.RDS")
